---
title: "Yolo Analysis"
author: "David L. White"
date: "`r format(Sys.time(), '%X, %Y-%m-%d')`"
output:
  html_document: default
  pdf_document: default
fig_width: 8 
fig_height: 8

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;', >
This document contains an analysis of the Lake Anna Beach and detections datasets. It includes data merging, aggregation, and linear regression analysis.
</p>
<br>
GitHub Repository: <a href="https://github.com/whitedl/prtm_yolo" target="_blank">https://github.com/whitedl/prtm_yolo</a>

</br>
</div>

```{r, Load_Pachages, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(ggplot2)
library(readr)
library(broom)  # For tidying model output
```


```{r, Read_Data, echo=FALSE, message=FALSE}
lake_anna_beach <- read_csv("~/Yolo_Code/prtm_yolo/datasets/Lake_Anna_Beach/Lake_Anna_Beach.csv")
detections <- read_csv("~/Yolo_Code/prtm_yolo/Code/detections_pivot_sum_by_class_beach.csv")
```


&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;', >
Table X. Input Lake Anna Count Data
</div>
<div style="overflow-y: scroll; height: 300px; width: 900px">
```{r, Print_Count_Data, echo=FALSE, message=FALSE}
# Display the table
knitr::kable(lake_anna_beach, caption = "")
```
</div>
</p>


&nbsp;
&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;', >
Table X. Yolo Detection Data
</div>
<div style="overflow-y: scroll; height: 300px; width: 900px">
```{r, Print_Detection_Data, echo=FALSE, message=FALSE}
# Display the table
knitr::kable(detections, caption = "")

```
</div>
</p>


&nbsp;
&nbsp;

```{r, Merge_Data, echo=FALSE, message=FALSE}
merged_data <- lake_anna_beach %>%
  inner_join(detections, by = c("File" = "filename"))

```
&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;', >
Table X. Merged Data with Counter Sum and Detection Sum (Human + People)
</div>
<div style="overflow-y: scroll; height: 300px; width: 900px">
```{r, Sum_Data, echo=FALSE, message=FALSE}
merged_data <- merged_data %>%
  mutate(Counter_sum = Counter0 + Counter1 + Counter2 + Counter3 + Counter4)
merged_data$Sum_Humans_People <- merged_data$Human + merged_data$People
knitr::kable(merged_data, caption = "")
```
</div>
</p>


&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;'>
Figure X. Time Series Counts and Detections
```{r, Plot_Data, echo=FALSE, message=FALSE}
merged_data$DateTime <- as.POSIXct(merged_data$DateTime, format="%Y-%m-%d %H:%M:%S")

ggplot(merged_data, aes(x = DateTime)) +
  geom_line(aes(y = Counter_sum, color = "Counters_People")) +
  geom_line(aes(y = Boat, color = "Boat")) +
  geom_line(aes(y = Human, color = "Human")) +
  geom_line(aes(y = People, color = "People")) +
  geom_line(aes(y = Sum_Humans_People, color = "Humans + People")) +
  labs(title = "",
       x = "DateTime",
       y = "Counts") +
  scale_color_manual(values = c("Counters_People" = "blue", "Boat" = "red", "Human" = "green", "People" = "purple", "Humans + People" = "black")) +
  theme_minimal()
```
</div>
</p>


&nbsp;
&nbsp;
```{r, Linear_Regression, echo=FALSE, message=FALSE}
lm_sum <- lm(Sum_Humans_People ~ Counter_sum, data = merged_data)
# summary(lm_sum)
```


<p>
<div style='font-size: 14px;'>
Table X. Summary of Linear Regression Model with R-squared and Adjusted R-squared
```{r, Linear_Regression_Summary_Table, echo=FALSE, message=FALSE}
# Tidy the model summary
lm_sum_tidy <- broom::tidy(lm_sum)

# Extract R-squared and Adjusted R-squared values
model_summary <- summary(lm_sum)
r_squared <- model_summary$r.squared
adj_r_squared <- model_summary$adj.r.squared

# Add R-squared and Adjusted R-squared to the tidy data frame
lm_sum_tidy <- lm_sum_tidy %>%
  add_row(term = "R-squared", estimate = r_squared, std.error = NA, statistic = NA, p.value = NA) %>%
  add_row(term = "Adjusted R-squared", estimate = adj_r_squared, std.error = NA, statistic = NA, p.value = NA)

# Display the table
knitr::kable(lm_sum_tidy, caption = "")

```
</div>
</p>

&nbsp;
&nbsp;
<p>
<div style='font-size: 14px;'>
Figure X. Linear Regression of Sum of Humans and People on Counter_sum
```{r, Plot_Linear_Regression, echo=FALSE, message=FALSE}
ggplot(merged_data, aes(x = Counter_sum, y = Sum_Humans_People)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "",
       x = "Counter_sum",
       y = "Sum of Humans and People") +
  theme_minimal()
```
</div>
</p>